Fast Nearest Neighbour Classification

### 2016-05-11 paper/paper.tex
finished

Every nearest neighbour search algorithm can be divided into two steps.
\paragraph{Preprocessing}
During the preprocessing the algorithm prepares the given set $\mathbb{S}$ for its needs.

@@

\begin{thebibliography}{4}
	\bibitem{url} Kenneth L. Clarkson, \"Nearest-Neighbor Searching and Metric Space Dimensions\" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
\end{thebibliography}

>>>>

Every nearest neighbour search algorithm can be divided into two steps.
\paragraph{Preprocessing}
During the preprocessing the algorithm prepares the given set $S$ for its needs.

@@

\begin{thebibliography}{4}
	\bibitem{url} Kenneth L. Clarkson, "Nearest-Neighbor Searching and Metric Space Dimensions" (October 2005), \url{http://kenclarkson.org/nn_survey/p.pdf}
\end{thebibliography}
